Check experimental design

### 2023-05-08 analysis/01_experimental-design.Rmd
aggregated-coded variables

>>>>

# Aggregate-coded interactions

We have a number of hypotheses referencing specific interactions. To answer these hypotheses, we need to specific each of the needed interactions. Here we do it by aggregating up the interaction terms.

```{r aggregate-interactions, warning=FALSE, message=FALSE}
# Convert the attributes in design into factors
interactions <- as.data.frame(design)
for(i in 4:ncol(interactions)) {
  interactions[,i] <- as.factor(interactions[,i])
}

# # Rename the variables
# colnames(interactions)[4:9] <- c("org", "issue", "transp", "account", "fund", "gov_rel")
# 
# # Use dummy_cols() to get an index-coded version of all the attribute levels
# interactions <- dummy_cols(
#   interactions, 
#   select_columns = c("org", "issue", "transp", "account", "fund", "gov_rel"),
#   remove_first_dummy = FALSE,
#   remove_selected_columns = TRUE
# )
# 
# # Rename the index-coded variables
# colnames(interactions)[4:21] <- c(
#   str_c("org", 1:4), str_c("issue", 1:4), str_c("transp", 1:2), 
#   str_c("account", 1:2), str_c("fund", 1:3), str_c("gov_rel", 1:3)
# )
#
# org1 = amnesty
# org2 = greenpeace
# org3 = oxfam
# org4 = redcross
# gov_rel1 = friendly
# gov_rel2 = criticized
# gov_rel3 = crackdown

# Build out all the necessary interactions...
# ...by multiplying together the needed index-coded levels.
interactions <- interactions %>% 
  as_tibble() %>% 
  mutate(
    h2b_1 = ifelse(Organization ==3|Organization==4, 1, 0), # 1 if org is oxfam or redcross
    h2b_2 = ifelse(`Relationship with host government` == 2|`Relationship with host government` == 3, 1, 0), # 1 if gov_rel is criticized or crackdown
    h2b_3 = h2b_1*h2b_2 # interaction term
    )
# interactions <- interactions %>% 
#   as_tibble() %>% 
#   mutate(
#     # Hypothesis 3b.
#     environment_criticized = issue2 * gov_rel2,
#     humanrights_criticized = issue3 * gov_rel2,
#     refugees_criticized = issue4 * gov_rel2,
#     environment_crackdown = issue2 * gov_rel3,
#     humanrights_crackdown = issue3 * gov_rel3,
#     refugees_crackdown = issue4 * gov_rel3,
#   )

# Save interact-coded design output
write.csv(interactions, here("data", "derived_data", "aggregate_interactions.csv"))
```
